Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-01-31 Paper/paper.tex
Some more paper edits

To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework byconstructing {\em sliding window embeddings} of our videos (Section~\ref{sec:slidingwindow}).  Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.  Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data \cite{traliehigh, tralie2017quasi}.  We autotune the sliding window size using fundamental frequency estimation \cite{Mcleod05asmarter}, and we use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} to find the appropriate spatial scale of the loop.  We then parameterize the video by assigning each window a phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.  We then re-order the sliding windows by phase and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which helps with drift (Section~\ref{sec:cyclereordering}).  As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e. single pixel grayscale video).  There are only 12 samples per period in the original signal, so the details of each period coarse and noisy.  However, once they are re-sorted, we get a nice, fine-detailed representation of one period.  The extension of this technique to videos will be described in detail in Section~\ref{sec:methods}.

Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, quantifying vocal fold anomalies in video \cite{tralie2017quasi}.  As shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop,

%The graph Laplacian, on the other hand, has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.  A different topological approach with cohomology circular coordinates\cite{de2011persistent} was used to parameterize a sliding window embedding of the .  Neural networks have also been trained to find circular coordinates \cite{levy2015live,anafi2017cyclops}.

@@

Talk about autotuning with peristent homology, mention that it's the opposite of the approach in \cite{bendich2011improving}.

>>>>

To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework byconstructing {\em sliding window embeddings} of our videos (Section~\ref{sec:slidingwindow}).  Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.  Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.  Furthermore, as shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop.  Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the temporal and spatial scales of the periodic motion, respectively, so that no user intervention is required.  Our embedding also makes it easy to assign each window a circular phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.  We then re-order the sliding windows by phase and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which further mitigates drift (Section~\ref{sec:cyclereordering}).  As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e. single pixel grayscale video).  There are only 12 samples per period in the original signal, so the details of each period coarse and noisy.  However, once they are re-sorted, we get a nice, fine-detailed representation of one period.  The extension of this technique to videos will be described in detail in Section~\ref{sec:methods}.

Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.  Our use of the graph Laplcian to parameterize time series is also unique, though we are inspired by works that have used it to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and works which use vector diffusion maps to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.  We use the combination of TDA + Laplacian eigenmaps as a simple alternative to the more complicated alternative cohomology circular coordinates \cite{de2011persistent}.

@@

Talk about autotuning with peristent homology, mention that it's the opposite of the approach in \cite{bendich2011improving}
